### 2021-02-23 evaluation.tex
Some small improvements

We used a \gls{gcn} as described in \cref{sec:architecture}
with depth 4, message size 16, \gls{relu} activation function,
residual connections and layer normalization.
We tuned the hyperparameters by a small manual grid search.
\todo[inline]{MS: zase pasivum. Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena. Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli. Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne. Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni. Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}

@@

A predicate symbol cost model is trained by gradient backpropagation
\todo{FB: Explain? MS: tohle by melo byt k pochopeni z predchozich sekci.}
on the precedence pair classification task
\todo{FB: Reference a section. MS: Ano!}
using the examples generated from the problems in $\ProblemsTrain$.
To avoid redundant computations, all examples generated from a problem are processed in the same training batch.
Thus, each training batch contains up to \num{128} problems and all the examples generated from these problems.
The symbol cost model is trained using the Adam optimizer \cite{Kingma2014}.
Learning rate starts at \num{1.28e-3}
and is halved each time the train loss stagnates for 10 consecutive epochs.
% tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)

@@

A predicate precedence recommender was trained on approximately \num{500000} examples,
% Half of the 1M predicate examples was used for validation.
and a function precedence recommender was trained on approximately \num{400000} examples.
% Half of the 800k function examples was used for validation.
For each problem $P \in \ProblemsVal$,
a pair\todo{MS: ja vim, ze sis to "vyplejtval" v predchozi vete,
ale kde jinde nez tady rict explicitne "predicate precendence" a "function precedence"?
Z toho "pair" ot nemusi byt jasny...}
 of symbol precedences was generated by the respective trained recommender
and \Vampire{} was run using these precedences
with a wall clock time limit of 10 seconds.
% Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
As a baseline, the performance of \Vampire{} with the \texttt{frequency} precedence heuristic was evaluated
with the same time limit.
For comparison, the two trained recommenders are evaluated separately,
with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.

>>>>

We used a \gls{gcn} described in \cref{sec:gcn}
with depth 4, message size 16, \gls{relu} activation function,
residual connections and layer normalization.
We tuned the hyperparameters by a small manual grid search.
\todo[inline]{MS: zase pasivum. Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena. Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli. Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne. Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni. Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}

@@

A predicate symbol cost model is trained by gradient descent
on the precedence pair classification task (described in \cref{sec:training})
using the examples generated from the problems in $\ProblemsTrain$.
To avoid redundant computations, all examples generated from a problem are processed in the same training batch.
Thus, each training batch contains up to \num{128} problems and all the examples generated from these problems.
The symbol cost model is trained using the Adam optimizer \cite{Kingma2014}.
Learning rate starts at \num{1.28e-3}
and is halved each time the train loss stagnates for 10 consecutive epochs.
% tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)

@@

A predicate precedence recommender was trained on approximately \num{500000} examples,
% Half of the 1M predicate examples was used for validation.
and a function precedence recommender was trained on approximately \num{400000} examples.
% Half of the 800k function examples was used for validation.
For each problem $P \in \ProblemsVal$,
a predicate and a function precedence
was generated by the respective trained recommender,
and \Vampire{} was run using these precedences
with a wall clock time limit of 10 seconds.
% Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
As a baseline, the performance of \Vampire{} with the \texttt{frequency} precedence heuristic was evaluated
with the same time limit.
For comparison, the two trained recommenders are evaluated separately,
with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.
